\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Umesh Gaikwad} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 9766185211 \\ Bengaluru, Karnataka, IN}
\address{\href{mailto:gaikwadumesh123@gmail.com}{gaikwadumesh123@gmail.com} \\ \href{https://www.linkedin.com/in/umeshg17/}{linkedin.com/in/umeshg17} \\ \href{https://umesh.skalekontrol.com}{umesh.skalekontrol.com}}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Summary}

{M.Tech CSA (IISc) engineer focused on reliable platform delivery at scale: multi-region EKS, Kubernetes operations, GitOps, and CI/CD (Jenkins, Argo CD). Emphasis on cost-aware design, observability, and automation with clear ownership. Seeking infrastructure, platform, or cloud engineering roles (IC).}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & Python, Bash; C (coursework) \\
Containers & Docker; Kubernetes (CKA); Helm; Karpenter (node/workload scaling) \\
Cloud & AWS (EKS, EC2, ALB/S3/IAM for workloads); GCP exposure (GKE, Dataproc) \\
IaC & Pulumi (primary at prior role), Terraform (modules / add-ons) \\
CI/CD & Jenkins, Bitbucket Pipelines, Argo CD; PR-reviewed Git workflows for infrastructure \\
Security & Kubernetes RBAC, workload identity patterns, image scanning in pipelines \\
Automation & REST/CLI tooling, Liquibase in pipelines, Slack-based deploy helpers \\
Observability & Metrics, logs, alerting; New Relic (NRQL); cost visibility (e.g., Kubecost) \\
Data (prior role) & Kafka, Spark \\
Learning & OpenShift (exploring)
\end{tabular}

\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{DevOps / Platform Engineer} \hfill Sep 2024 -- Present\\
Observe.AI \hfill \textit{Bengaluru, Karnataka, IN}

\begin{itemize}
    \itemsep -3pt {} 
    \item Managed 15+ multi-region EKS production clusters with 100+ microservices --- node pool isolation, Karpenter autoscaling, PDBs, and resource right-sizing.
    \item Delivered 175+ production infrastructure changes with zero downtime through a structured change-management process.
    \item Owned Jenkins CI/CD on Kubernetes --- multi-EKS agents, ALB ingress, Okta SSO, observability integrations, and pipeline tuning for faster builds.
    \item Built a Jira-gated Terraform plan/apply pipeline with AI-powered risk review, S3 plan storage, Slack notifications, and auto-cancellation --- changes applied only after approval reaches the deployment window.
    \item Built an AI-powered Slack bot for fast AWS resource lookups in incidents --- natural-language queries across accounts via LangGraph agents and MCP, reducing console context switching.
    \item Designed an approval-based Snowflake change workflow with Liquibase --- PR validation, CODEOWNERS, CI/CD integration, and auditable schema changes.
\end{itemize}


 
\textbf{DevOps Engineer} \hfill Aug 2023 -- Sep 2024\\
Amagi Media Labs \hfill \textit{Bengaluru, Karnataka, IN}

\begin{itemize}
    \itemsep -3pt {} 
    \item Shipped GitOps improvements with Argo CD --- image scanning and policy checks before promotion to target environments.
    \item Ran staged Kubernetes upgrades and add-on rollouts with health checks and documented rollback paths.
    \item Rolled out AWS Load Balancer Controller and ingress for predictable routing to internal services.
    \item Built Slack-backed tooling for guarded, on-demand deploys with a lightweight audit trail (who/when/what).
    \item Partnered with SRE to add dashboards and alerts for PRs, releases, and cloud spend alongside on-call practices.
    \item Shipped infrastructure changes using the platform team's standardized Pulumi stacks.
\end{itemize}

\textbf{Teaching Assistant} \hfill Aug 2022 -- Apr 2023\\
Indian Institute of Science \hfill \textit{Bengaluru}

\begin{itemize}
    \itemsep -3pt {}
    \item E0 225 (\textit{Design \& Analysis of Algorithms}): tutorials and evaluation; cohort of 80+ students.
    \item E0 208 (\textit{Computational Geometry}): evaluation and invigilation; cohort of 60+ students.
\end{itemize}


\textbf{Big Data Engineer} \hfill July 2019 -- Apr 2020\\
Exadatum \hfill \textit{Pune, Maharashtra, IN}

\begin{itemize}
    \itemsep -3pt {}
    \item Built a Docker-based Spark + Livy setup for notebook-driven jobs so the team could iterate before paying for Dataproc clusters.
    \item Consolidated related Java modules and added JUnit coverage around Kafka $\rightarrow$ GCS ingestion paths.
    \item Delivered POCs across Dataproc/Livy REST, GKE deploy scripts (logs to GCS), and multi-user JupyterHub (details on request).
\end{itemize}


\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Selected public work}

\begin{itemize}
    \itemsep -3pt {}
    \item \textbf{jenkins-k8s-agent-helm} --- Jenkins inbound agents on Kubernetes (WebSocket, IRSA, optional Karpenter). \href{https://github.com/SkaleKontrol/jenkins-k8s-agent-helm}{github.com/SkaleKontrol/jenkins-k8s-agent-helm}
    \item \textbf{ECR + Bottlerocket EBS snapshot} --- encrypted volume snapshot with image pre-pull for faster EKS node bring-up. \href{https://github.com/SkaleKontrol/ecr-bottlerocket-ebs-snapshot}{github.com/SkaleKontrol/ecr-bottlerocket-ebs-snapshot}
    \item \textbf{klabctl} --- kubeadm-based multi-node Kubernetes lab on Multipass. \href{https://github.com/SkaleKontrol/klabctl}{github.com/SkaleKontrol/klabctl}
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{PROJECTS}
% \vspace{-1.25em}
% \item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
% \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
% \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
% \end{rSection} 

%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Curricular Activities} 
% \begin{itemize}
%     \item	Sample extracurricular bullet (edit or delete this section). 
%     \item	Sample bullet point.
% \end{itemize}


% \end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications \& Achievements} 
\begin{itemize}
    \item \textbf{GATE 2021}: Top 2\% among $\sim$200k candidates (GATE CS paper); admitted to IISc Bangalore (M.Tech CSA).
    \item \href{https://www.credly.com/badges/75d9811c-198b-4dc5-a41d-dd3a6e6d9ee3/public_url}{Google IT Automation with Python – Coursera Professional Certificate}
    \item \href{https://www.credly.com/badges/5e298069-3cc7-4a4b-b30c-79a8ae8f624f/public_url}{Certified Kubernetes Administrator (CKA)}
\end{itemize}

\end{rSection}

\begin{rSection}{Education}

{\bf Master of Technology -- Computer Science and Automation}, IISc Bangalore \hfill { July 2023}
\begin{itemize}
    \item Relevant coursework: Network and Distributed Systems Security, Principles of Distributed Software, Scalable Systems for Data Science.
    \item Coursework and readings on distributed systems, fault tolerance, storage, and messaging at scale.
    \item Teaching Assistant, \textit{Computational Geometry}: graded work and supported 100+ students (UG, M.Tech, Ph.D.) with timely feedback on assignments.
\end{itemize}

{\bf Bachelor of Engineering - Computer Science}, MGM's COE Nanded \hfill {July 2019}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
\begin{itemize}
    \item Relevant coursework: Data Structures and Algorithms, Operating Systems, Computer Networks, Database Management Systems.
    \item C and Python used across coursework, labs, and small projects.
\end{itemize}

\end{rSection}

\end{document}

